### 2013-09-18 manuscripts/reply/reply.tex
Adding to reply.
Adding coin-flip example.

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \subset
\allParameterValues$ such that $p(\theta)$ describes our belief that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \subset
\allParameterValues$ and $\alignment{}{} \subset \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
        \myTheta{})p(\myTheta{})}{p(\alignment{i}{}},
    \label{eq:bayesrule}
\end{equation}
where $p(\alignment{i}{}) = \int{\myTheta{}} p(\alignment{i}{} \given
\myTheta{})p(\myTheta{}) d\myTheta{}$.
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

Now, this is not to say that empirical Bayesian approaches not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citp[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods are often a powerful means of parameter
estimation that display favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often display good frequentist coverage behavior
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

@@

@@

\section*{Differing utilities of \numt{} and \vmratio{} in \msb}
We preface this section with a clarification of an issue that has
been confused throughout the \msb literature.
The mean (\meant{}), variance (\vart{}), and dispersion index
($\vart{}/\meant{} = \vmratio{}$) of divergence times are \emph{not} parameters
of the model implemented in \msb.
Rather they are statistics that summarize parameters of the model.
This is in contrast to \numt{}, which is a parameter of the model.

@@

>>>>

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \subset
\allParameterValues$ such that $p(\theta)$ describes our belief that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \subset
\allParameterValues$ and $\alignment{}{} \subset \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
    \myTheta{})p(\myTheta{})}{p(\alignment{i}{})},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{}) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{})p(\myTheta{}) d\myTheta{}.
\end{equation}
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

Now, this is not to say that empirical Bayesian approaches not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods are often a powerful means of parameter
estimation that display favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often display good frequentist coverage behavior
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

@@

This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the United States' quarter dollar unfair.
That is to say that our null hypothesis is that the probability of a US quarter
landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while the tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given their prior knowledge that Joe moonlights as a magician, and is notorious
for performing coin and card tricks in the lab, they suspect there is a good
chance that Joe will use his slight-of-hand skills to replace their quarter
with one of his two-headed or two-tailed coins he has up his sleeve at all
times.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

Mary calls Joe into the lab, and hands him a regular-issue US quarter minted in
1992.
After five tosses, four of which was heads, Joe decides that academics are
crazy and leaves the lab to pursue a major in theatre.  Mary and Will, both
being computational biologists, are satisfied with their
empirical dataset of $y = 4$ heads out of $N = 5$ trials.
They know from the conjugacy of the beta prior, that the posterior distribution
has the nice analytical form $\theta|y,N \sim beta(a + y, b + N - y)$, which
in this case is simply $beta(4.5, 1.5)$; this is the true posterior distribution
of $\theta$ given their prior belief and data (Figure~\ref{figCoinFlip}).
This allows them to plug these values into the beta cumulative distribution
function to determine that the posterior probability of their hypothesis is
$p(\theta < 0.5 | y=1, N=5) = 0.088$.
Given their prior belief and dataset, this indeed is the correct posterior
probability of the hypothesis, and Mary and Will should now update their
posterior belief accordingly.

However, upon reflecting on the results of their experiment
(Figure~\ref{figCoinFlip}), Mary and Will regret not trusting Joe to refrain
from turning their experiment into a magic trick.
Their prior looks very ``poorly selected,'' and if they had only
had more faith in Joe's integrity, they would have selected a much better
prior. Clearly form their results, they should have used a prior centered
around 0.2; their data suggest a prior of $beta(4.5, 1.5)$ would have been
much more appropriate.
Rather than resort to flipping the coin five more times, Mary and Will decide
to redo their analysis using the much better ``prior'' of $p(\theta) \sim
beta(4.5, 1.5)$.
This gives a ``posterior'' of $\theta|y,N \sim beta(8.5, 2.5)$, and a
probability of their hypothesis of $p(\theta < 0.5 | y=1, N=5) = 0.026$.
Now convinced that the mass of President Washington's head renders the US
Quarter unfair, Will begins composing an e-mail of complaint for the U.S.\
Mint.

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better estimator for the parameter \myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirical informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.

@@

\section*{Differing utilities of \numt{} and \vmratio{} in \msb}
We preface this section with a clarification of an issue that has
been confused throughout the \msb literature.
The mean (\meant{}{}), variance (\vart{}{}), and dispersion index
($\vart{}{}/\meant{}{} = \vmratio{}$) of divergence times are \emph{not} parameters
of the model implemented in \msb.
Rather they are statistics that summarize parameters of the model.
This is in contrast to \numt{}, which is a parameter of the model.

@@

\mFigure{../images/coin_flip.pdf}{
    A plot of three beta density functions meant to represent a prior
    (black), true posterior (blue), and empirical Bayes density (red).
}{figCoinFlip}
